\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{geometry}

% Geometry
\geometry{left=1.5cm, right=1.5cm, top=1.5cm, bottom=1.5cm}

% Font: Helvetica (Sans Serif) - Cleaner look
\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault} 
\usepackage[T1]{fontenc}

% Custom Colors
\usepackage{xcolor}
\definecolor{primary}{RGB}{0, 77, 153} % Dark Blue

% Formatting
\titleformat{\section}{\Large\bfseries\color{primary}\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{8pt}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \textbf{V. SHAHITH KUMAR}} \\ \vspace{4pt}
    \small 
    \faEnvelope \ \href{mailto:shahithu2004@gmail.com}{shahithu2004@gmail.com} $|$ 
    \faPhone \ +916301103526 
            $|$ \faLink \ LinkedIn | GitHub
    \end{center}

%-----------SUMMARY-----------
\section{Professional Summary}
Results-driven Python developer with 4+ years of experience in financial services, leveraging expertise in Python, SQL, and data pipelines to drive high-impact trading strategies and data-driven decision-making.

%-----------EXPERIENCE-----------
\section{Experience}
\begin{itemize}[leftmargin=0.15in, label={}]
        \resumeSubheading
      {Extion Infotech}{None}
      {Data Science Intern}{}
            \begin{itemize}
                \resumeItem{Analyzed datasets using Python and SQL to deliver useful insights.}
                \resumeItem{Developed machine learning models and deep learning solutions.}
                \resumeItem{Automated data preprocessing and feature engineering workflows.}
                \resumeItem{Collaborated with teams to understand business needs and build solutions.}
                \resumeItem{Created Power BI dashboards to visualize findings clearly.}
                \resumeItem{Managed GitHub-based workflows to maintain clean and organized projects.}
              \end{itemize}
          \end{itemize}

%-----------EDUCATION-----------
\section{Education}
\begin{itemize}[leftmargin=0.15in, label={}]
        \resumeSubheading
      {None}{None}
      {None}{}
    \end{itemize}

%-----------PROJECTS-----------
\section{Projects}
\begin{itemize}[leftmargin=0.15in, label={}]
        \resumeSubheading
      {AI Data Analytics Dashboard}{}
      {Flask, Pandas, NumPy, Scikit-learn, Matplotlib, Seaborn, HTML, CSS, JavaScript}{}
            \begin{itemize}
                \resumeItem{Built a Flask web app that lets users upload CSV/Excel files and quickly analyze data.}
                \resumeItem{Automatically cleaned data by fixing columns, removing errors, and detecting abnormal values.}
                \resumeItem{Created simple charts like histograms, box plots, bar charts, and heatmaps for easy understanding.}
                \resumeItem{Added real-time updates using SocketIO to make the dashboard feel live and interactive.}
                \resumeItem{Built a RandomForest prediction system to help users forecast values and test what-if scenarios.}
                \resumeItem{Allowed users to download cleaned data and results as CSV/Excel files.}
              \end{itemize}
              \resumeSubheading
      {TravelBuddy: AI-Powered Travel Recommendation \& Trip Planning System}{}
      {Flask, Pandas, NumPy, Scikit-learn, Matplotlib, Seaborn, HTML, CSS, JavaScript}{}
            \begin{itemize}
                \resumeItem{Built a Flask web app that lets users upload CSV/Excel files and instantly analyze their data.}
                \resumeItem{Cleaned data automatically by fixing column names, handling missing values, and detecting unusual data.}
                \resumeItem{Created charts like histograms, box plots, bar charts, and heatmaps for easy understanding.}
                \resumeItem{Added real-time updates using SocketIO so the dashboard feels live and interactive.}
                \resumeItem{Built a prediction system using RandomForest to help users forecast values and run simple what-if scenarios.}
                \resumeItem{Added export options so users can download cleaned data or results as CSV/Excel.}
              \end{itemize}
          \end{itemize}

%-----------SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \small{
     \textbf{Languages \& Tools:}\ Programming: Python; Database: SQL; Machine Learning: Predictive Modeling, Model Training, Model Evaluation; Data Engineering: ETL Pipelines, Data Modeling; Data Visualization: Power BI, Matplotlib; AI/ML Application Development: Flask; Tools \& Practices: Git, GitHub, Jupyter Notebook; Data Products: Real-time Data Systems, Automation-Oriented AI Solutions; Data Products: Data Pipelines for High-Performance Trading
    }
\end{itemize}

%-----------CERTIFICATIONS-----------
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
        \item \small{{'name': 'Complete Data Science Bootcamp', 'issuer': 'Udemy', 'desc': 'Python, SQL, Excel, Machine Learning, Data Analytics'}}
        \item \small{{'name': 'DOTNET Full Stack Certification', 'issuer': 'Wipro TalentNext', 'desc': 'C\\#, SQL, Full Stack Development Fundamentals'}}
    \end{itemize}

\end{document}